Global Climate and Atmospheric Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and \Spitzer\ Phase Curve Observations

### 2018-04-04 ApJ_submit_v2/response.txt

1       x
2       x
3       x
4       x
5	x
6       x
7       x
8       x
9       x
10	x
11      x
12
13
14      x-abstract
15
16      x
17      x
18
19	x
20      x
21      x
22      x
23

@@

8. Section 3.4: The authors mention that the RMS of the white light curve was larger than predicted based on the photon noise and the spectral curves. The suggested option "imperfect modeling of the astrophysical signal or instrumental systematics" is too generic a statement and should be deleted. Also, the loss of flux outside of the extraction window option is only relevant for the most blue and most red spectral bins. The authors state that they do not further explore this as the wavelength dependent data do reach the photon limit.

I disagree with this approach. The fact that if you divide up the data into enough bins that systematic effects are no longer significant does not make them unimportant - especially when conclusions are being drawn from the total spectrum which is obtained by using all of the data. If the white light curve does not follow the photon noise limit, then this implies that excess noise in each wavelength bin (while not significant on its own), is adding constructively with that from other bins. This might imply a color dependent systematic, which would affect the results presented here.

More discussion here is warranted to show conclusively that the larger than predicted noise is not biasing the data or results. (This may be as simple as showing that other works show similar effects or that there are other works with elevated red noise in all channels but have shown that this does not affect the end results).

This is a good point, and something that concerned us as well. We endeavor to explain more clearly here why our inferences about the spectroscopic light curves are not affected by the additional noise in the white light curve.

One point (that we mentioned but not in great detail) is that the white light curve is more strong affected by loss of light off the detector edge than the spectroscopic light curves. The spectrum moves slightly on the detector over the course of a visit. We correct for this shift by interpolating the spectrum onto a common wavelength scale. However, we cannot correct for any flux lost off the edge of the detector. Flux loss at the edge is relevant for the white light curve, since it encapsulates all the flux, but does not affect the spectroscopic light curves, which are limited in wavelength range and do not extend all the way to the edge. In general we find that our rms is very sensitive to the size of our extraction window, so we think this effect is a plausible explanation for additional noise in the white light curve.

Another important consideration that we neglected to mention is that the astrophysical signal is wavelength dependent -- the eclipse depths increase by 50% from the bluest channel to the reddest channel.  But for the white light curve, we sum up the whole signal and fit it with a single phase curve model. Therefore, we expect a systematic scatter in the phase curve due to the wavelength dependence of the astrophysical signal.

A final point is that there are multiple cases of exoplanet transmission spectra measured with WFC3 that are consistent with a flat line at higher precision than what we measure here (e.g. Kreidberg et al. 2014). If wavelength-dependent systematic noise were present in data from this detector, it would be very challenging to measure a flat spectrum (you would have to conspire to have the planet signal cancel out the instrumental effects). There is nothing unusual about our data set (the fluence level and scan rate are very comparable to what has been observed before), so it is reasonable to expect that our data does not suffer from a systematic bias.

### 2018-04-04 ApJ_submit_v2/ms.tex
point 11

\subsection{Goodness of Fit}
\label{sec:fitquality}
%WFC3 white: obs, exp rms (ppm) 172.140941477 122.002526515
%Ch1: rms obs, exp (ppm) 766.79959876 470.309808368
%Ch2: rms obs, exp (ppm) 636.908048707 639.675550854
We performed several tests of the quality of the light curve fits.  First we predicted the level of scatter in the light curves based on photon noise alone, then compared this value to the root-mean-square (rms) of the fit residuals.  For the spherical harmonics fit to the phase variation, the Spitzer 4.5 $\mu$m light curve rms reaches the expected photon noise limit (637 versus 640 ppm). The 3.6 $\mu$m light curve has significantly larger rms (767 versus 470 ppm), due to time-correlated red noise (discussed below). The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 ppm, and the measured rms was typically within 5\% of expectations for all spectroscopic channels.  For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (172 versus 122 ppm). There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, loss of flux outside the extraction window, and imperfect modeling of the astrophysical signal or instrument systematics. However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (where we reach the photon limit), so we do not further explore the small excess noise in the white light curve.

>>>>

\subsection{Goodness of Fit}
\label{sec:fitquality}
%WFC3 white: obs, exp rms (ppm) 172.140941477 122.002526515
%Ch1: rms obs, exp (ppm) 766.79959876 470.309808368
%Ch2: rms obs, exp (ppm) 636.908048707 639.675550854
We performed several tests of the quality of the light curve fits.  First we predicted the level of scatter in the light curves based on photon noise alone, then compared this value to the root-mean-square (rms) of the fit residuals.  For the spherical harmonics fit to the phase variation, the Spitzer 4.5 $\mu$m light curve rms reaches the expected photon noise limit (637 versus 640 ppm). The 3.6 $\mu$m light curve has significantly larger rms (767 versus 470 ppm), due to time-correlated red noise (discussed below). The expected photon-limited rms for the WFC3 spectrosopic light curves ranges from 430 - 530 ppm, and the measured rms was typically within 5\% of expectations for all spectroscopic channels.  For the WFC3 band-integrated white light curve, the rms was slightly larger than predicted (172 versus 122 ppm). There are a number of possible origins for this discrepancy, including imperfect background subtraction, variation in the position of the spatial scan on the detector, and loss of flux outside the extraction window. \added{In addition, the amplitude of the phase variation increases by 50\% over the WFC3 wavelength range, which leads to a small increase in the noise in the white light curve. To make an order of magnitude estimate for the amplitude of this effect, we calculate the standard deviation of the secondary eclipse depths in all wavelength channels. It is $\sim100$ ppm, which is comparable to the additional scatter we observed FIxme}

However, our analysis of the composition and thermal structure of the planet's atmosphere is based on the wavelength-dependent data (where we reach the photon limit), so we do not further explore the small excess noise in the white light curve.
